Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-10 paper/main.tex
[issue 0.3, 1.2, 2.7] shorten sections

\item{Reflection:
We flip each image horizontally with a probability of 0.5 to exploit mirror symmetry. }
\item{Translation:
We also have translational symmetry in the images.
Given an image of size $48\times48$ pixels, we extract a random contiguous crop
of size $44\times44$.
Each cropping is equivalent to randomly shifting a $44\times44$ image by up to 4 pixels
vertically and/or horizontally. }
\item{Gaussian noise:
We introduce random Gaussian noise to each pixel values
by using a similar method to \cite{krizhevsky2012imagenet}.}
\end{itemize}
\changed{
In addition to artificially increasing the size of the dataset,
these data augmentation schemes make the resulting model more invariant to
rotation, reflection, translation, and small noise in the pixel values.
We also note that the data augmentation steps
}
add almost no computational cost,
as they are performed on the CPU while the GPU is training the ConvNets on images.

@@

To make final classifications,
we use our ConvNet model to make 64 sets of predictions for
64 transformations of the input images:
4 rotations, 4 horizontal translations, and 4 vertical translations
(with random horizontal reflections).
Although we use an identical network architecture for all transformations,
we consider each set of predictions as separate results from different models.
Finally, we use a model combination technique known as
Bayesian Model Combination~\citep[BMC;][]{Monteith2011}, which
uses Bayesian principles to generate an ensemble combination of different models.
Although the data augmentation step in Section~\ref{sec:data_augmentation} should
make our ConvNet model invariant to these types of transformations,
we find that applying BMC still results in a significant increase in performance.

The posterior probability that a source is a galaxy is given by
\begin{equation} \label{eq:posterior_bmc}
  P \left(G | \bmath{x}, \bmath{D}, \bmath{M}, \bmath{E} \right)
  = \sum_{e \in \bmath{E}} P \left(G | \bmath{x}, \bmath{M}, e \right)
  P \left(e | \bmath{D} \right),
\end{equation}
where $\bmath{x}$ is the input, $\bmath{D}$ is the data set,
$\bmath{M}$ is the set of models (\ie different transformations of input images),
and $e$ is an element in the ensemble space $\bmath{E}$ of possible model combinations.
By Bayes' Theorem, the posterior probability of $e$ given $\bmath{D}$ is given by
\begin{equation} \label{eq:p_ensemble}
  P \left(e | \bmath{D} \right)
  = \frac{P \left(e \right)}{P \left(\bmath{D} \right)}
  \prod_{d \in \bmath{D}} P \left( d | e \right)
  \propto P \left(e\right) \prod_{d \in \bmath{D}} P \left(d | e \right).
\end{equation}
Here, $P\left(e \right)$ is the prior probability of $e$,
which we assume to be uniform.
The product of $P\left(d | e\right)$ is
over all individual data $d$ in the training data $\bmath{D}$,
and $P\left(\bmath{D}\right)$ is merely a normalization factor
and not important.
For probabilistic classifiers,
we can directly use the probabilistic predictions
and write Equation~\ref{eq:p_ensemble} as
\begin{equation} \label{eq:p_ensemble_prob}
  P \left( e | \bmath{D} \right) \propto 
  P \left( e \right) \prod_{i=1}^{N}
  \hat{y}_i y_i + 
  \left(1 - \hat{y}_i\right) \left(1 - y_i\right).
\end{equation}

Although the space $\bmath{E}$ of potential model combinations
is in principle infinite,
we can produce a reasonable finite set
of potential model combinations by using sampling techniques.
In our implementation,
the weights of each combination of the base classifiers
is obtained by sampling from a Dirichlet distribution.
We first set all alpha values of a Dirichlet distribution to unity.
We then sample this distribution $q$ times
to obtain $q$ sets of weights.
For each combination,
we assume a uniform prior and
calculate $P\left(e|\bmath{D}\right)$ using
Equation~\ref{eq:p_ensemble_prob}.
We select the combination with the highest $P\left(e|\bmath{D}\right)$,
and update the alpha values by
adding the weights of the most probable combination
to the current alpha values.
The next $q$ sets of weights are drawn
using the updated alpha values.

We continue the sampling process until
we reach a predefined number of combinations,
and we finally use Equation~\ref{eq:posterior_bmc} to compute
the posterior probability that a source is a star (or a galaxy).
In this paper, we use a $q$ value of three,
and we consider a total of 1,000 model combinations.

>>>>

\item{Reflection:
We flip each image horizontally with a probability of 0.5 to exploit mirror symmetry. }
\item{Translation:
We also have translational symmetry in the images.
Given an image of size $48\times48$ pixels, we extract a random contiguous crop
of size $44\times44$.
Each cropping is equivalent to randomly shifting a $44\times44$ image by up to 4 pixels
vertically and/or horizontally. }
\item{Gaussian noise:
We introduce random Gaussian noise to each pixel values
by using a similar method to \cite{krizhevsky2012imagenet}.}
\end{itemize}
\changed{
In addition to artificially increasing the size of the data set,
these data augmentation schemes make the resulting model more invariant to
rotation, reflection, translation, and small noise in the pixel values.
We also note that the data augmentation steps
}
add almost no computational cost,
as they are performed on the CPU while the GPU is training the ConvNets on images.

@@

To make final classifications,
we use our ConvNet model to make 64 sets of predictions for
64 transformations of the input images:
4 rotations, 4 horizontal translations, and 4 vertical translations
(with random horizontal reflections).
Although we use an identical network architecture for all transformations,
we consider each set of predictions as separate results from different models.
Finally, we use a model combination technique known as
Bayesian Model Combination~\citep[BMC;][]{Monteith2011}, which
uses Bayesian principles to generate an ensemble combination of different models.
Although the data augmentation step in Section~\ref{sec:data_augmentation} should
make our ConvNet model invariant to these types of transformations,
we find that applying BMC still results in a significant increase in performance.
\changed{
Although a complete description of BMC is beyond the scope of this paper,
we provide a brief description.
For more details, we refer the reader to \citet{Monteith2011}.
}

\sout{ The posterior probability that a source is a galaxy is given by }
\sout{ $ P \left(G | \bmath{x}, \bmath{D}, \bmath{M}, \bmath{E} \right) = \sum_{e \in \bmath{E}} P \left(G | \bmath{x}, \bmath{M}, e \right) P \left(e | \bmath{D} \right), $ }
\sout{ where $\bmath{x}$ is the input, $\bmath{D}$ is the data set, $\bmath{M}$ is the set of models (\ie different transformations of input images), and $e$ is an element in the ensemble space $\bmath{E}$ of possible model combinations.  By Bayes' Theorem, the posterior probability of $e$ given $\bmath{D}$ is given by }
\sout{$ P \left(e | \bmath{D} \right) = \frac{P \left(e \right)}{P \left(\bmath{D} \right)} \prod_{d \in \bmath{D}} P \left( d | e \right) \propto P \left(e\right) \prod_{d \in \bmath{D}} P \left(d | e \right). $}
\sout{Here, $P\left(e \right)$ is the prior probability of $e$, which we assume to be uniform.  The product of $P\left(d | e\right)$ is over all individual data $d$ in the training data $\bmath{D}$, and $P\left(\bmath{D}\right)$ is merely a normalization factor and not important.  For probabilistic classifiers, we can directly use the probabilistic predictions and write Equation~\ref{eq:p_ensemble} as}
\sout{ $ P \left( e | \bmath{D} \right) \propto P \left( e \right) \prod_{i=1}^{N} \hat{y}_i y_i + \left(1 - \hat{y}_i\right) \left(1 - y_i\right), $}

\sout{Although the space $\bmath{E}$ of potential model combinations is in principle infinite, we can produce a reasonable finite set of potential model combinations by using sampling techniques.  In our implementation, the weights of each combination of the base classifiers is obtained by sampling from a Dirichlet distribution.  We first set all alpha values of a Dirichlet distribution to unity.  We then sample this distribution $q$ times to obtain $q$ sets of weights.  For each combination, we assume a uniform prior and calculate $P\left(e|\bmath{D}\right)$ using Equation~\ref{eq:p_ensemble_prob}.  We select the combination with the highest $P\left(e|\bmath{D}\right)$, and update the alpha values by adding the weights of the most probable combination to the current alpha values.  The next $q$ sets of weights are drawn using the updated alpha values.}

\sout{We continue the sampling process until we reach a predefined number of combinations, and we finally use Equation~\ref{eq:posterior_bmc} to compute the posterior probability that a source is a star (or a galaxy).  In this paper, we use a $q$ value of three, and we consider a total of 1,000 model combinations.}
